%%% Compile using: pdflatex main.tex %%%
\documentclass[a4paper,12pt]{article}
\usepackage{mypackages}

\title{\textbf{MNXB01} - Project report}
\date{\today}
\author{Cameron Robertson, \and Viktor Drugge, \and Louise Villander}

\begin{document}
	\maketitle
	\section{Introduction}
	\label{sec:pre}
	In this report, urban adjusted temperatures from the Uppsala data center will be analysed
	and graphed, with a particular focus on Spring temperatures. Samples of temperatures during certain
	days will also be plotted. Finally, the data will be used to determine the beginning of Spring, through
	the temperature definition. To do this, ROOT version 5.34/30 is used.
	\input{./camreport/myreport}
	\input{viktor}
	\input{louise}
	
	\section{Conclusion}
	\label{sec:con}
	This report has demonstrated some of the results from analysis of the Uppsala dataset. Despite the sporadic nature of temperature when 
	taken over a long period of time, we have seen that viable conclusions and results can be derived. The mean temperature of a given day was seen to be quite variable depending on 
	which day was inputted, but the general trend over a number of days was as expected (increase throughout late March). Interestingly, extracting the spring date of each year
	suggested March 20th or March 21th as the average date of spring arrival, in line with the commonly accepted date. Plotting the temperature of all determined dates resulted in a 
	histogram that fitted well with a exponential function, this is as expected since on average the temperature increase gradually each spring. Leap years shift dates after the 28th
	of february which affect the results, but this is of minor concern since the standard deviation is relatively high, even when shifting the dates by one day. Plotting the mean temperatures
	of every day shows how much temperatures vary over the course of a year, and also that temperatures can vary quite a lot from year to year on the same date, particularly during the end 
	of winter and in spring.
\end{document}
